%-------------------------
% Author: Kuldeep
% My modified version of resume in LaTeX,
% based on https://github.com/jakegut/resume
% License : MIT
%------------------------

\newcommand{\myName}{Kuldeep Parmar}
\newcommand{\myPhoneNumber}{6355720306}
\newcommand{\myEmail}{hey@kuldeep.tech}
\newcommand{\myGithub}{github.com/coldter}
\newcommand{\myLocation}{Rajkot, Gujarat}
\newcommand{\myCityTzSlug}{rajkot}
\newcommand{\myWebsite}{kuldeep.tech}

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage[a4paper,margin=0.85in,footskip=0.0in]{geometry}
\usepackage{fancyhdr}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemm}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemListHeading}[1]{
  \small{
    {\vspace{10pt} \hspace{-16pt} \textbf{#1}: \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
  \textbf{\Huge \scshape \myName} \\ \vspace{5pt}
  \small
  % {\myPhoneNumber} $|$
  {\expandafter\href\expandafter{tel:+91\myPhoneNumber}{\underline{+91 \myPhoneNumber}}} $|$
  {\expandafter\href\expandafter{mailto:\myEmail}{\underline{\myEmail}}} $|$
  {\expandafter\href\expandafter{https://\myWebsite}{\underline{\myWebsite}}} $|$
  {\expandafter\href\expandafter{https://\myGithub}{\underline{\myGithub}}} $|$
  {\expandafter\href\expandafter{https://www.timeanddate.com/time/zone/india/\myCityTzSlug}{\underline{\myLocation}}}
\end{center}

%          -ABOUT

\section{About}
\begin{adjustwidth}{8pt}{4pt}
  \hspace{35pt}
  \small{I'm a passionate software developer with strong problem-solving skills and deep interest in the ever-growing world of cloud-native tech, with a keen focus on information security to build beautiful and secure solutions. Willing to work remotely with teams to embrace new challenges and achieve success.}
\end{adjustwidth}
%-----------EXPERIENCE-----------
\section{Work Experience}
% C-2
\resumeSubHeadingListStart
\resumeSubheading
{Backend Developer \& DevOps}{Jan 2024 -- Present} % From RESUME_DATA.work[0]
{Freelancing}{Gujarat, India} % From RESUME_DATA.work[0] and RESUME_DATA.location
\resumeItem{ % This outer \resumeItem wraps the list of bullet points
  \resumeItemListStart
  \resumeItem{Managed end-to-end project lifecycle for various clients, from requirements gathering and solution design to deployment and post-launch support.}
  \resumeItem{Collaborated with clients as a key resource for maintaining and scaling diverse platforms, including an on-demand food delivery system with a large codebase and numerous entities.}
  \resumeItem{Leveraged Node.js and its ecosystem to develop robust RESTful APIs and backend services tailored to specific client needs and business logic.}
  \resumeItem{Developed custom software solutions and automation scripts, including the integration of AI-powered APIs (e.g., for text processing, data enrichment, or intelligent routing) to meet unique client requirements.}
  \resumeItem{Integrated solutions such as AWS CloudFront, Redis cache, and monitoring services (Sentry, CloudWatch) into client platforms to significantly enhance performance, scalability, and reliability.}
  \resumeItem{Dockerized diverse services and managed/maintained over 20 servers across various cloud platforms (AWS, DigitalOcean) for multiple client projects, ensuring high availability.}
  \resumeItem{Built a high-volume PDF generation service using Puppeteer and AWS Lambda for clients, enabling the creation of large, data-driven PDFs from various aggregated sources.}
  \resumeItem{Provided technical consulting on cloud architecture, security best practices (including assisting with security audits and compliance requirements), and performance optimization strategies.}
  \resumeItem{Actively maintained comprehensive project documentation, architectural diagrams, and wikis for client engagements to ensure clarity, smooth handovers, and knowledge transfer.}
  \resumeItem{Utilized the Cloudflare platform extensively (DNS, CDN, WAF, Workers, KV, Pages, etc.) to implement serverless solutions, enhance application security, and improve global content delivery for various client projects.}
  \resumeItemListEnd
}
% C-1
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
\resumeSubheading
{Backend Developer}{Feb 2022 -- Dec 2024}
{Rbian Infotech}{Gujarat, India}
\resumeItem{
  \resumeItemListStart
  \resumeItem{I worked as a key part of the backend development leveraging technologies like Node.js, TypeScript, MongoDB, PostgreSQL, message queues, etc. to build scalable solutions for high traffic and cloud environments.}
  \resumeItem{Provisioned and maintained cloud infrastructure like provisioning of Ec2, Loadbalancers, VPC, RDS, S3, etc.}
  \resumeItem{Developed a git based documentation system for engineers to easily collaborate and document various part of the projects and codebase, decreasing time in onboarding and knowledge transfer.}
  \resumeItem{Migrated legacy es5 codebase to typescript and implemented tests for critical parts using frameworks like jest, resulting in better maintainability with quicker development cycles.}
  \resumeItem{Worked on various POCs for new feature and for project development from the ground up with high focus deliverability and fast iteration.}
  \resumeItem{Help in implementing and troubleshoot CI/CD pipelines for various projects with code review systems.}
  \resumeItem{Utilized docker and devcontainer to standardize development environment across team member, along with linters like ESLint and prettier to maintain code quality and consistency across projects.}
  \resumeItemListEnd
}
\resumeSubHeadingListEnd

% %-----------PROJECTS-----------
% \section{Projects}
% \resumeSubHeadingListStart
% \resumeProjectHeading
% {\textbf{Checkers} $|$ \emph
%   {Java, Typescript, Maven}
% }
% {\small{\href
%     {https://github.com/Moztanku/Checkers}
%     {\underline{github.com/Moztanku/Checkers}}
%   }}
% \resumeItemListStart
% \resumeItem{Client-server checkers application with multiple playable variants}
% \resumeItem{Server written in Java and web client made in TypeScript}
% \resumeItem{Communication via WebSocket with decoder/encoder written by me in Java}
% \resumeItemListEnd

% \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Atmiya University}{Gujarat, India}
{Bachelor Of Science in Information Tech}{2019 -- 2022} %{}
% \resumeItemListStart
% \resumeItemListHeading{Relevant coursework}
% \resumeItem{Algorithms and Data Structures}
% \resumeItem{Metaheuristic Algorithms}
% \resumeItem{Programming Languages and Paradigms}
% \resumeItemListEnd
\resumeSubHeadingListEnd

% %           -LANGUAGES-

% \section{Languages}
% \begin{itemize}[leftmargin=0.15in, label={}]
%   \small{\item{
%         \textbf{English}{: Communicative (B2)} \\
%         \textbf{Gujarati}{: Native} \\
%         }}
% \end{itemize}
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Technologies}{:
          Golang,
          TypeScript,
          JavaScript,
          Python,
          Node.js,
          Deno,
          Git,
          Linux,
          AWS,
          Docker,
          MongoDB,
          PostgreSQL,
          MySQL,
          Redis,
          Websockets,
          Socket.io,
          CI/CD,
          GitHub Actions,
          AI/ML API Integration
        } \\
        \textbf{Interests}{:
          Information Security,
          Cloud Computing,
          DevOps,
          Serverless,
          Distributed Systems,
          Open Source
        } \\
        \textbf{Miscellaneous:}{
          \underline{Born:} November 2000
        } \\

        }}
\end{itemize}
%-------------------------------------------

%           -FOOTER-

\AtBeginShipoutNext{%
  \AtBeginShipoutUpperLeft{%
    \put(35,-835){% Adjust these coordinates
      \parbox{\textwidth}{\fontsize{6.5}{1}\selectfont
        \textit{I agree to the processing of personal data provided in this document for the purpose of the recruitment process in accordance with the provisions of the Information Technology (Reasonable Security Practices and Procedures and Sensitive Personal Data or Information) Rules, 2011 under the Information Technology Act, 2000, and in agreement with any other applicable laws and regulations in India pertaining to the protection of personal data.}}%
    }%
  }%
}

\end{document}